Supplement 3.1

### 2023-03-14 Code/Manuscript_figures.Rmd
updated figures after coauthor review

Fig1.A <-ggplot() +
  geom_line(data=filter(obs_data, grouping=="State/Territory/DC"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=0.85) +
  scale_x_date(date_labels="%b-%y", breaks = obs_data$date, date_breaks ="3 months", date_minor_breaks ="1 month") +
  geom_line(data=filter(obs_data, grouping=="National"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=1.25) +
  geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
  scale_colour_manual(name="",
                      values = c("National"="black",
                                 "State/Territory/DC"="grey75")) +
  labs(title = "A. Reported Cases Per 100K Population",
       y = "Incident COVID-19 Cases") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.02, 0.82),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA)) + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

@@

WIS.heatmap <-mean_WIS %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage") +
  theme(axis.title.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

all_subs <-subs_nat %>%
  bind_rows(., subs_state) %>% 
  mutate(model_reorder=factor(model, levels=levels_model), 
         key=factor(key, levels=levels_key),
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  bind_rows(., missings) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

Fig7B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

>>>>

Fig1.A <-ggplot() +
  geom_line(data=filter(obs_data, grouping=="State/Territory/DC"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=0.85) +
  scale_x_date(date_labels="%b-%y", breaks = obs_data$date, date_breaks ="3 months", date_minor_breaks ="1 month") +
  geom_line(data=filter(obs_data, grouping=="National"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=1.25) +
  geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
  scale_colour_manual(name="",
                      values = c("National"="black",
                                 "State/Territory/DC"="grey75")) +
  labs(title = "A. Reported Cases Per 100K Population",
       y = "Incident COVID-19 Cases per 100K population") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.02, 0.82),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA)) + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

@@

WIS.heatmap <-mean_WIS %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score",
       title="B. Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage",
       title="C. 95% Coverage") +
  theme(axis.title.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

all_subs <-subs_nat %>%
  bind_rows(., subs_state) %>% 
  mutate(model_reorder=factor(model, levels=levels_model), 
         key=factor(key, levels=levels_key),
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  bind_rows(., missings) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted",
       title="A. Percent of Weeks Submitted") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

Fig7B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*80% CI is lower than baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

### 2023-03-14 Code/Supplement 1A_figures.Rmd
updated figures after coauthor review

nat_st %>%
  dplyr::select(-target, -target_end_date, -value) %>%
  distinct() %>%
  group_by(sub_date, model) %>%
  summarize(locs=n()) %>%
  ungroup() %>%
  mutate(log_loc=log(locs)) %>%
  ungroup() %>%
  mutate(total_sub=length(unique(sub_date))) %>%
  group_by(model) %>%
  mutate(wks_sub=length(sub_date),
         per_sub=wks_sub/total_sub) %>%
  ungroup() %>%
  left_join(., teams_nat_st, by="model") %>%
  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
         model_rename=fct_reorder(model_rename, wks_sub)) %>%
  ggplot(., aes(sub_date, model_rename)) +
  geom_tile(aes(fill=log_loc)) +
  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d") + 
  geom_text(aes(label=locs), size=1.50) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
  theme_bw() +
  labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
       subtitle= "The number of locations forecasted per submission is labled",
       caption = "*Model met inclusion criteria") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        legend.position = "none")

>>>>

nat_st %>%
  dplyr::select(-target, -target_end_date, -value) %>%
  distinct() %>%
  group_by(sub_date, model) %>%
  summarize(locs=n()) %>%
  ungroup() %>%
  mutate(log_loc=log(locs)) %>%
  ungroup() %>%
  mutate(total_sub=length(unique(sub_date))) %>%
  group_by(model) %>%
  mutate(wks_sub=length(sub_date),
         per_sub=wks_sub/total_sub) %>%
  ungroup() %>%
  left_join(., teams_nat_st, by="model") %>%
  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
         model_rename=fct_reorder(model_rename, wks_sub)) %>%
  ggplot(., aes(sub_date, model_rename)) +
  geom_tile(aes(fill=log_loc)) +
  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d",
                      name = "Number of \nlocations forecasted", 
                      breaks = c(0, 3.9), 
                      labels =c(1, 50)
                      ) + 
 # geom_text(aes(label=locs), size=1.50) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
  theme_bw() +
  labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
       #subtitle= "The number of locations forecasted per submission is labled"#,
       caption = "*Model met inclusion criteria"
       ) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        legend.position = "bottom", legend.title.align=0.5)

### 2023-03-14 Code/Supplement 1B_figures.Rmd
updated figures after coauthor review

library(gridExtra)

@@

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

@@

@@

counts %>%
  dplyr::select(-target, -target_end_date, -value) %>%
  distinct() %>%
  group_by(sub_date, model, pop_size_quant2) %>%
  summarize(locs=n()) %>%
  rename_counts() %>%
  ungroup() %>%
  mutate(log_loc=log(locs)) %>%
  mutate(total_sub=length(unique(sub_date))) %>%
  ungroup() %>%
  group_by(model, pop_size_quant2) %>%
  mutate(wks_sub=length(sub_date),
         per_sub=wks_sub/total_sub) %>%
  ungroup() %>%
  left_join(., all_dat, by="model") %>%
  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
         model_rename=fct_reorder(model_rename, wks_sub)) %>%
  ggplot(., aes(sub_date, model_rename)) +
  geom_tile(aes(fill=per_sub)) +
  scale_fill_gradient(low = "#c7e9c0", high = "#4a1486",
                      name="Percent of \nCounties \nForecasted") + 
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
  facet_wrap(~ pop_size_quant2) +
  theme_bw() +
  labs(title = "B. Primary Model* Submissions for County-Level Case Forecasts Over Time",
       caption = "*Model met inclusion criteria") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        strip.background = strip.background_standard, strip.text = strip.text_standard,
        legend.position = "bottom")

>>>>

library(gridExtra)
library(grid)

@@

@@

## Function for setting up legends in empty facet spaces
library(gtable)
library(cowplot)

shift_legend <- function(p){

  # check if p is a valid object
  if(!"gtable" %in% class(p)){
    if("ggplot" %in% class(p)){
      gp <- ggplotGrob(p) # convert to grob
    } else {
      message("This is neither a ggplot object nor a grob generated from ggplotGrob. Returning original plot.")
      return(p)
    }
  } else {
    gp <- p
  }

  # check for unfilled facet panels
  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
  empty.facet.panels <- sapply(facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]]))
  empty.facet.panels <- facet.panels[empty.facet.panels]
  if(length(empty.facet.panels) == 0){
    message("There are no unfilled facet panels to shift legend into. Returning original plot.")
    return(p)
  }

  # establish extent of unfilled facet panels (including any axis cells in between)
  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
  empty.facet.panels <- list(min(empty.facet.panels[["t"]]), min(empty.facet.panels[["l"]]),
                             max(empty.facet.panels[["b"]]), max(empty.facet.panels[["r"]]))
  names(empty.facet.panels) <- c("t", "l", "b", "r")

  # extract legend & copy over to location of unfilled facet panels
  guide.grob <- which(gp[["layout"]][["name"]] == "guide-box")
  if(length(guide.grob) == 0){
    message("There is no legend present. Returning original plot.")
    return(p)
  }
  gp <- gtable_add_grob(x = gp,
                        grobs = gp[["grobs"]][[guide.grob]],
                        t = empty.facet.panels[["t"]],
                        l = empty.facet.panels[["l"]],
                        b = empty.facet.panels[["b"]],
                        r = empty.facet.panels[["r"]],
                        name = "new-guide-box")

  # squash the original guide box's row / column (whichever applicable)
  # & empty its cell
  guide.grob <- gp[["layout"]][guide.grob, ]
  if(guide.grob[["l"]] == guide.grob[["r"]]){
    gp <- gtable_squash_cols(gp, cols = guide.grob[["l"]])
  }
  if(guide.grob[["t"]] == guide.grob[["b"]]){
    gp <- gtable_squash_rows(gp, rows = guide.grob[["t"]])
  }
  gp <- gtable_remove_grobs(gp, "guide-box")

  return(gp)
}

@@

counts_subs <-counts %>%
  dplyr::select(-target, -target_end_date, -value) %>%
  distinct() %>%
  group_by(sub_date, model, pop_size_quant2) %>%
  summarize(locs=n()) %>%
  rename_counts() %>%
  ungroup() %>%
  mutate(log_loc=log(locs)) %>%
  mutate(total_sub=length(unique(sub_date))) %>%
  ungroup() %>%
  group_by(model, pop_size_quant2) %>%
  mutate(wks_sub=length(sub_date),
         per_sub=wks_sub/total_sub) %>%
  ungroup() %>%
  left_join(., all_dat, by="model") %>%
  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
         model_rename=fct_reorder(model_rename, wks_sub)) %>%
  ggplot(., aes(sub_date, model_rename)) +
  geom_tile(aes(fill=per_sub)) +
  scale_fill_gradient(low = "#c7e9c0", high = "#4a1486",
                      name="Percent of \nCounties \nForecasted") + 
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
  facet_wrap(~ pop_size_quant2) +
  theme_bw() +
  labs(title = "B. Primary Model* Submissions for County-Level Case Forecasts Over Time",
       caption = "*Model met inclusion criteria") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        strip.background = strip.background_standard, strip.text = strip.text_standard,
        legend.position = "bottom")

grid.draw(shift_legend(counts_subs))

### 2023-03-14 Code/Supplement 2_Outliers.Rmd
updated figures after coauthor review

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

>>>>

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*80% CI is lower than baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

### 2023-03-14 Code/Supplement 2_Revisions.Rmd
updated figures after coauthor review

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(#axis.title.y=axis.title.y_standard,
    legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())#, axis.text.y=element_blank())

>>>>

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*80% CI is lower than baseline") + 
  theme_bw() +
  theme(#axis.title.y=axis.title.y_standard,
    legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())#, axis.text.y=element_blank())

### 2023-03-14 Code/Supplement 3.1_figure.rmd
updated figures after coauthor review

WIS.heatmap <-mean_WIS %>%
  ungroup() %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=scaled_rel_skill)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), axis.text.y=element_blank(),
        axis.title.y = element_blank(), axis.text=axis.text_standard,
        legend.position="bottom")

@@

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=mean_count)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

all_subs <-subs_co %>%
  bind_rows(., subs_co_other) %>%
  mutate(key=pop_size_quant2,
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  ungroup() %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>%  
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model)) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted") +
  theme(axis.title.x = element_blank(),   
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

>>>>

WIS.heatmap <-mean_WIS %>%
  ungroup() %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=scaled_rel_skill)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score",
       title="B. Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), axis.text.y=element_blank(),
        axis.title.y = element_blank(), axis.text=axis.text_standard,
        legend.position="bottom")

@@

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=mean_count)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage",
       title="C. 95% Coverage") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

@@

all_subs <-subs_co %>%
  bind_rows(., subs_co_other) %>%
  mutate(key=pop_size_quant2,
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  ungroup() %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>%  
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model)) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted",
       title="A. Percent of Weeks Submitted") +
  theme(axis.title.x = element_blank(),   
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")
